### 2023-12-24 documentation/thesis/thesis_document.tex
.

\begin{itemize}
\tightlist
\item
  usb, ethernet
\item
  pps input output
\item
  multiplexer for i2c sensors alredy implemented
\item
  imput / output for sync
\end{itemize}

@@

These cover all the required functions described in the
Usecases\ref{usecases}. The biggest distinguishing feature, apart from
the sensor used, is the \passthrough{\lstinline!scan mode!}. In this
context, this describes whether the sensor can measure a
\passthrough{\lstinline!static!} fixed point on the magnet or if the
sensor can move \passthrough{\lstinline!dynamically!} around the magnet
using a controllable manipulator.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_1D_sensor_contrsuction_with_universal_magnet_mount.png}
\caption{1D sensor contrsuction with universal magnet mount
\label{1D_sensor_contrsuction_with_universal_magnet_mount.png}}
\end{figure}

The \passthrough{\lstinline!1D!}
sensor\ref{1D_sensor_contrsuction_with_universal_magnet_mount.png} is
the simplest possible sensor that is compatible with the
\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} platform
and also with the \gls{mrp}-library\ref{software-readout-framework}.

>>>>

\begin{figure}
\centering
\includegraphics{./generated_images/border_1D_sensor_schematic_and_circuit_board.png}
\caption{1D sensor schematic and circuit board
\label{1D_sensor_schematic_and_circuit_board.png}}
\end{figure}

\ref{1D_sensor_schematic_and_circuit_board.png}

\begin{itemize}
\tightlist
\item
  usb
\item
  multiplexer for i2c sensors alredy implemented
\item
  imput / output for sync
\end{itemize}

@@

These cover all the required functions described in the
Usecases\ref{usecases}. The most important difference, apart from the
sensor used, is the \passthrough{\lstinline!scan mode!}. In this
context, this describes whether the sensor can measure a
\passthrough{\lstinline!static!} fixed point on the magnet or if the
sensor can move \passthrough{\lstinline!dynamically!} around the magnet
using a controllable manipulator.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_1D_sensor_construction_with_universal_magnet_mount.png}
\caption{1D sensor construction with universal magnet mount
\label{1D_sensor_construction_with_universal_magnet_mount.png}}
\end{figure}

The \passthrough{\lstinline!1D!}
sensor\ref{1D_sensor_construction_with_universal_magnet_mount.png} is
the simplest possible sensor that is compatible with the
\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} platform
and also with the \gls{mrp}-library\ref{software-readout-framework}.
